---
title: "Stats for DS HW 3"
author: "Matthew DeSantis"
date: '2022-09-20'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 2.3.15

## (a)
```{r}
48/choose(52,5)
```
## (b)
```{r}
choose(4,2)*choose(4,2)*44/choose(52,5)
```
## (c)
```{r}
choose(4,3)*choose(12,2)*4*4/choose(52,5)
```
\newpage

# 2.4.6

## (a)
E1 and not E2. This is equal to P(E1) - P(E1 and E2).
```{r}
0.95 - 0.88
```
## (b)
E2 and not E1. This is equal to P(E2) - P(E2 and E1).
```{r}
0.92 - 0.88
```
## (c)
(E1 and not E2) or (E2 and not E1). This is equal to the sum of the answers from (a) and (b).
```{r}
(0.95-0.88)+(0.92-0.88)
```
## (d)
E1 or E2. This is equal to P(E1) + P(E2) - P(E1 and E2).
```{r}
0.95+0.92-0.88
```
\newpage

# 2.5.12

## (a)
E1 = Aircraft is discovered = 0.7. E2 = Aircraft has locator. P(E2 | E1) = 0.6. P(E2 | not E1) = 0.1.
P(E2 and not E1) = P(E2 | not E1)\*P(not E1) =
```{r}
0.1*0.3
```
## (b)
P(E2) = P(E1)\*P(E2 | E1) + P(not E1)\*P(E2 | not E1) =
```{r}
(0.7*0.6) + (0.3*0.1)
```
## (C)
P(not E1 | E2) = (P(not E1)\*P(E2 | not E1))/(P(not E1)\*P(E2 | not E1) + P(E1)\*P(E2 | E1)) = 
```{r}
(0.3*0.1)/((0.3*0.1)+(0.7*0.6))
```
\newpage

# 2.6.7

## (a)
```{r echo = F, results='asis'}
library(knitr)
sports = data.frame(Football = c(0.3,0,0.3), 
                   Basketball = c(0.22,0.28,0.5), 
                   Track = c(0.13,0.07,0.2), 
                   Total = c(0.65, 0.35, 1))
rownames(sports) = c("Male", "Female", "Total")
kable(sports, caption = "Sports Preferences by Gender")
```
## (b)
P(Female | Basketball) = P(Female and Basketball)/P(Basketball) =
```{r}
0.28/0.5
```
## (c)
No. Because P(F | B) != P(F), (0.56 != 0.5), by definition, they are not independent.
\newpage

# 3.2.4
```{r}
total = choose(10,3)
PMF = data.frame(zero = c(choose(7,3)/total),
                 one = c(choose(3,1)*choose(7,2)/total),
                 two = c(choose(3,2)*choose(7,1)/total),
                 three = c(choose(3,3)/total)
                )
rownames(PMF) = c("P(X=x)")
kable(PMF, caption = "PMF")
CDF = data.frame(zero = c(choose(7,3)/total),
                 one = c(choose(3,1)*choose(7,2)/total+choose(7,3)/total),
                 two = c(choose(3,2)*choose(7,1)/total+
                           choose(3,1)*choose(7,2)/total+choose(7,3)/total),
                 three = c(choose(3,3)/total+choose(3,2)*choose(7,1)/total+
                             choose(3,1)*choose(7,2)/total+choose(7,3)/total)
                )
rownames(CDF) = c("P(X=x)")
kable(CDF, caption = "CDF")
```
\newpage

# 3.2.8

## (a)
```{r}
checkout_CDF = function(x) {
  if (x<=0){
    return (0)
  }
  
  if (0<x && x<=2) {
    return ((x**2)/4)  
  }
  
  else {
    return (1)
  }
}

checkout_CDF(1)-checkout_CDF(0.5)
```
## (b)
The PDF can be obtained from the CDF by integrating with respect to x. Doing so in this case results in
f(x) = x/2 for x between 0 and 2, 0 otherwise. 

## (c)
To derive these, substitute y/60 for x. Therefore, the CDF is ((y/60)^2)/4 is:
CDF of Y = (y^2)/14400 for y between 0 and 120, 0 otherwise.
Taking the derivative, we get 
PDF of Y = y/7200 for y between 0 and 2, 0 for x<=0, and 1 for x>120.