---
title: "Stats for DS HW 2"
author: "Matthew DeSantis"
date: '2022-09-15'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

"1.6.16"

a: units are thousands of dollars for mean and thousands of dollars squared for variance. Values as shown below.
```{r}
salaries = c(152,169,178,179,185,188,195,196,198,203,204,209,210,212,214)
meansal = mean(salaries)
varsal = var(salaries)
meansal
varsal
```
b (i):
```{r}
newvar = varsal
newmean = meansal + 5
newmean
newvar
```
b (ii):
```{r}
newvar2 = (1.05**2)*varsal
newmean2 = 1.05*meansal
#doing it another way to verify
salaries2 = 1.05*salaries

newmean2
mean(salaries2)
newvar2
var(salaries2)
```
\newpage
"1.7.4"

a:
```{r tidy = FALSE}
si=read.table(
url(
"https://media.pearsoncmg.com/cmg/pmmg_mml_shared/mathstatsresources/Akritas/SolarIntensAuData.txt"),
header=T)
boxplot(si)
```
b:
```{r}
quantile(si$SI, .3)
quantile(si$SI, .6)
quantile(si$SI, .9)
```
\newpage
"2.2.10"

a: E1 has 21, E2 has 14, E3 has 30

c: (1)E1 and E2: The disk has low shock absorption and low hardness
   (2)E1 or E2: The disk has low shock absorption or low hardness or both
   (3)E1 - E2: The disk has low hardness and high shock absorption
   (4)(E1 - E2) or (E2 - E1): The disk has low hardness and high shock absorption or the disk has high hardness and low                              shock absorption
   
d: (1) has 5, (2) has 30, (3) has 16, (4) has 25
\newpage
"2.3.9"

a:
```{r}
choose(12, 4)
```

b:
```{r}
(choose(5,2)*4*3)
```

c: 120/495