---
title: "Stats for DS HW 5"
author: "Matthew DeSantis"
date: "2022-10-05"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 3.4.8

## (a)

negative binomial

## (b)

sample space = {5,6,7,...}

PMF = f(x) = choose(x-1, 4)(0.05^5)(0.95^(x-5))

## (c)
```{r}
1 - pnbinom(35, 5, 0.05)
```

\newpage

# 3.4.19

## (a)

Var(X1) = 2.6, Var(X2) = 3.8

## (b)
```{r}
0.6*(dpois(0, 2.6))+0.4*(dpois(0,3.8))
```
## (c)

P(by X2 | no errors) = P(by X2 and no errors)/P(no errors) = 
```{r}
0.4*dpois(0,3.8)/(0.6*(dpois(0, 2.6))+0.4*(dpois(0,3.8)))
```

\newpage

# 3.5.1 

## (a)
```{r}
1 - pexp(4, 1/6)
```
## (b)
variance = 1/36
```{r}
qexp(0.95, 1/6)
```
## (c)

### (i)
```{r}
1 - pexp(5, 1/6)
```
### (ii)
6 years, because the exponential distribution is memoryless.

\newpage

# 3.5.8

## (a)
```{r}
1 - pnorm(600, 500, 80)
```
## (b)
```{r}
qnorm(0.99, 500, 80)
```

\newpage

# 4.2.3

## (a)
```{r}
0.15+0.135+0.12+0.3
0.12+0.135
```
## (b)
f(x) = 0.42 for x=8, 0.31 for x=10, 0.27 for x=12, 0 otherwise
f(y) = 0.48 for y=1.5, 0.405 for y=2, 0.115 for y=2.5

## (c)
```{r}
(.135+.12)/(.135+.12+.15)
```

\newpage

# 4.2.8

## (a)
Solving the double integral with bounds 0 to 1.5 and x to 3-x (2e^(-x-y)) dydx results in 1-4e^-3 or about 0.80

## (b)
marginal pdf of y is f(y) = (-2e^(-y))*((-2e^(-y))-1) for y>=0.
marginal pdf of x is f(x) = 2e^(-2x) for x>=0
