---
title: "Stats for DS HW 8"
author: "Matthew DeSantis"
date: "2022-11-02"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 5.4.5

X is the height of randomly selected segment. X has mean 36 and variance 1/12. Because the number is large (>=30), we can say (by the central limit theorem) that the mean height of a tower (the sum of 30 segments) is approximately normally distributed ~N(30\*36, 30\*1/12). The difference of the two towers' heights would then be approximately N~(0, 5). The chance that this is less than 4 and greater than -4 would be as given in the R code. Because this is based on the CLT, this is an approximation. 

```{r}
pnorm(4,0,sqrt(5))-pnorm(-4,0,sqrt(5))
```
\newpage

# Additional Problem 1

Y = ln(X) -> X = exp(Y) for exp(Y) > 0 (which is everywhere) \newline
fy(y) = exp(y-exp(y)) for negative infinity < y < positive infinity

\newpage

# Additional Problem 2

Inverses: X1=Y1/Y2, X2=Y2 \newline
Jacobian: (1/Y2)(1) + (-Y1/Y2^2)(0) = 1/Y1 \newline
Bounds: 0<Y1<Y2<1 \newline
fY1,Y2(y1,y2) = (Y1/Y2^2)+1 for 0<Y1<Y2<1

\newpage

# Additional Problem 3

## (a)
```{r}
set.seed(488103)
n = 100000
X1 = runif(n)
X2 = runif(n)
Y = c()
for(x in 1:n){
  Y = append(Y, max(X1[x], X2[x]))
}
CDF = function(x){
  length(Y[Y<=x])/n
}
CDF(0.5)
CDF(0.75)
```

## (b)
```{r}
hist(Y)
```